Reducing Acceptance Marks in Emerson-Lei Automata by QBF-solving

### 2022-04-26 paper/main.tex
intro percentage

\begin{abstract}
  \emph{Transition-based Emerson-Lei automata (TELA)} became a popular
  formalism that generalizes many traditional kinds of automata over
  infinite words including Büchi, co-Büchi, Rabin, Streett, and parity
  automata. Transitions in a TELA are labelled with acceptance marks
  and its accepting formula is a positive Boolean combination of terms
  saying that a particular mark has to be visited infinitely or
  finitely often. % in an accepting run.
  Algorithms processing these automata are often very sensitive to the
  number of %different
  acceptance marks. We introduce a new technique reducing the number
  of %different
  acceptance marks in TELA with use of \emph{quantified Boolean
    formulas (QBF)}.
  % : if a constructed QBF formula is satisfiable then
  % its model encodes an equivalent accepting formula with less
  % acceptance marks.
  In fact, we present three formula constructions
  % trading speed for higher reduction efficiency.
  with increasing reduction potential and formula complexity, and thus
  also decreasing speed of their satisfiability solving. We evaluated
  our reduction technique on TELA produced by state-of-the-art tools
  of the libraries Owl and Spot and by the tool \texttt{ltl3tela}. The
  technique reduced some acceptance marks in automata produced by all
  the tools. On automata with more than one acceptance mark produced
  by tools Delag and Rabinizer~4 of the Owl library, our technique reduced
  reduced 27.5\% and 38.4\% of acceptance marks, respectively. \todo{zkontrolovat!}
  % The achieved
  % reduction of acceptance marks on automata produced by tools of the Owl library was
  % between 25 and 40\%.
\end{abstract}

>>>>

\begin{abstract}
  \emph{Transition-based Emerson-Lei automata (TELA)} became a popular
  formalism that generalizes many traditional kinds of automata over
  infinite words including Büchi, co-Büchi, Rabin, Streett, and parity
  automata. Transitions in a TELA are labelled with acceptance marks
  and its accepting formula is a positive Boolean combination of terms
  saying that a particular mark has to be visited infinitely or
  finitely often. % in an accepting run.
  Algorithms processing these automata are often very sensitive to the
  number of %different
  acceptance marks. We introduce a new technique reducing the number
  of %different
  acceptance marks in TELA with use of \emph{quantified Boolean
    formulas (QBF)}.
  % : if a constructed QBF formula is satisfiable then
  % its model encodes an equivalent accepting formula with less
  % acceptance marks.
  In fact, we present three formula constructions
  % trading speed for higher reduction efficiency.
  with increasing reduction potential and formula complexity, and thus
  also decreasing speed of their satisfiability solving. We evaluated
  our reduction technique on TELA produced by state-of-the-art tools
  of the libraries Owl and Spot and by the tool \texttt{ltl3tela}. The
  technique reduced some acceptance marks in automata produced by all
  the tools. On automata with more than one acceptance mark produced
  by tools Delag and Rabinizer~4 of the Owl library, our technique reduced
  reduced 29.1\% and 38.5\% of acceptance marks, respectively.
  % The achieved
  % reduction of acceptance marks on automata produced by tools of the Owl library was
  % between 25 and 40\%.
\end{abstract}
